MHF SCP Experiment Visualisations

### 2024-08-06 minos/outcomes/MHF_SCP_visualisations.Rmd
Added more summary functions for recalculating relative and absolute poverty groups each year

compare_relative_absolute <- function(comparison_scen) {
  scen.list <- c('baseline', comparison_scen)

@@

>>>>

compare_relative_absolute <- function(comparison_scen, kids = FALSE) {

  scen.list <- c('baseline', comparison_scen)

  if (kids) {
    UC.rel <- do.call(rbind, generate_df_list('UC_kids_rel_pov', scen.list))
    UC.abs <- do.call(rbind, generate_df_list('UC_kids_abs_pov', scen.list))
  } else {
    UC.rel <- do.call(rbind, generate_df_list('UC_rel_pov', scen.list))
    UC.abs <- do.call(rbind, generate_df_list('UC_abs_pov', scen.list))
  }

@@

## Families with Children

```{r}
compare_relative_absolute(comparison_scen = '25UniversalCredit', kids=TRUE)
compare_relative_absolute(comparison_scen = '50UniversalCredit', kids=TRUE)
compare_relative_absolute(comparison_scen = '70UniversalCredit', kids=TRUE)
compare_relative_absolute(comparison_scen = '100UniversalCredit', kids=TRUE)
```
